Making Sequential Programs Deterministic

### 2019-03-27 design.tex
precision rules

\subsection{Determinism checker specific rules for precision}\label{precision}
We annotated the \codieid{equals()} method of the \<Set> class in the JDK as
\begin{verbatim}
PolyDet$\uparrow$ boolean equals(PolyDet Set<E> this, PolyDet Object o)
\end{verbatim}
While this is sound, it is imprecise in the case of \codeid{OrderNonDet Sets}. We added the following rule shown in Figure~\ref{fig-precision-rules} to our checker to improve precision:

\begin{figure}
    \todo{linebreak}
    $\infer{\Gamma \vdash \mathit{z : Det}}{\Gamma \vdash \mathit{x} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{x} \ \beta_{x}\rangle, \mathit{y} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{y} \ \beta_{y}\rangle & \mathit{z = x.equals(y)} & \langle \kappa_{x} \ \beta_{x}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle & \langle \kappa_{y} \ \beta_{y}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle }$

@@

\begin{itemize}
    \item Problem with \<Map.get()> : Annotating as \<@PolyDet> is imprecise.
    \item We circumvent this by hardcoding rules to make it precise. (Describe the rule here)

    \item We annotate System.getProperty as \<@NonDet> because the results could vary across machines.
    \item Exceptions: line.Separator, file.Separator. and path.Separator.
    \item discuss type on Exceptions and unsoundness due to this.
\end{itemize}

>>>>

\subsection{Determinism checker specific rules for precision}\label{precision}
We annotated the \codieid{equals()} method of the \<Set> class in the JDK as
\begin{verbatim}
PolyDet$\uparrow$ boolean equals(PolyDet Set<E> this, PolyDet Object o)
\end{verbatim}
While this is sound, it is imprecise in the case of \codeid{OrderNonDet Sets}. We added the following rule shown in Figure~\ref{fig-precision-rules} to our checker to improve precision.
\begin{figure}
    \todo{linebreak}
    $\infer[\sc{\mathit{SET \ PRECISION}}]{\Gamma \vdash \mathit{z : Det}}{\Gamma \vdash \mathit{x} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{x} \ \beta_{x}\rangle, \mathit{y} : \mathit{OrderNonDet} \ \mathit{Set}\langle \kappa_{y} \ \beta_{y}\rangle & \mathit{z = x.equals(y)} & \langle \kappa_{x} \ \beta_{x}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle & \langle \kappa_{y} \ \beta_{y}\rangle \nsqsubseteq \langle \mathit{OrderNonDet \ List} \rangle }$

    $\infer[\sc{\mathit{MAP \ PRECISION}}]{\Gamma \vdash \mathit{z : Det}}{\Gamma \vdash \mathit{x : OrderNonDet \ Map\langle Det \ \beta_k, \kappa_v\ \beta_v \rangle, y : Det \ \beta} & \mathit{z = x.get(y)}}$

@@

Similarly, the \codeid{get()} method in the \<Map> class is annotated with polymorphic annotations and the rule $\sc{\mathit{MAP \ PRECISION}}$ in Figure~\ref{fig-precision-rules} improves precision for \<OrderNonDet> receivers.

\codeid{System.getProperty()} returns a \<NonDet> type since we can't provide any determinism guarantees for
executions across machines. However, we make exceptions when the argument to this method is one of 
\codeid{"line.separator", "path.separator", or "file.separator"} as they return OS dependent values which are guaranteed to be deterministic on that OS.
